<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Prediction of Readmission for Diabetic Patients

<!-- badges: start -->
[![R-CMD-check](https://github.com/Lynn9358/LinearRegression-R/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Lynn9358/LinearRegression-R/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Lynn9358/LinearRegression-R/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Lynn9358/LinearRegression-R?branch=main)
  <!-- badges: end -->
<!-- badges: end -->


## backgrouds

## Overview

Linear regression model in R is a package for simple and multiple linear model fitting, providing a set of verbs that help to solve common model fitting challenges. 

-   `LRM_R()` fits linear regression model using least squares method, displays the overall result of fitted regression model, calculates the estimated value，standard deviation and statistics value and confidence intervals of coefficients.


## Installation

You can install the development version of LinearRegressionR from [GitHub](https://github.com/) with:

```r
# install.packages("devtools")
devtools::install_github("Lynn9358/LinearRegression-R")
```

## Usage

```r
library ("LinearRegressionR")
```

## Example

This is a basic example of Linear Regression:
``` {r}
library(LinearRegressionR)
## basic example code
LRM_R(mtcars$mpg~mtcars$disp +mtcars$wt+mtcars$qsec )
``` 

To fit with actual value
``` {r}
#Dataset from an experiment on measuring the reaction velocity versus substrate concentration in an enzymatic reaction involving untreated cells or cells treated with Puromycin.
df_Puromycin = Puromycin[order(Puromycin$conc),]
y_real = df_Puromycin$conc
y_model = LRM_R(df_Puromycin$conc~df_Puromycin$rate +df_Puromycin$state)$Y_model
plot(y_real,type="l",col="red")
lines(y_model,col="green")
```
## missing values
Delete variable Weight, Payer code, Medical specialty and unknown/invalid rows in Gender.


## Reference

Methods in this package  mainly stem from [Introduction to Linear Regression Analysis](https://ebookcentral.proquest.com/lib/umichigan/detail.action?docID=7103892o)
